Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
minor typo

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results from whole-brain GLM
analyses of the movie and the audio-description to a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from
naturalistic auditory stimulation to the individual PPA localization
with a block-design stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Additional analyses of the robustness of the results presented here
are available as supplementary materials.

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14
participants and a unilateral right clusters in two participants
\citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for
each naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrasts, in comparison to the results of a conventional
block-design localizer (unthresholded $Z$-maps are provided on NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five participants,
a unilateral right cluster in six participants (of which one participant yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the block-design
localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine participants that are within or overlapping with the block-design localizer results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in the
left-hemispheric PPA.

>>>>

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compared results from whole-brain GLM
analyses of the movie and the audio-description to a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compared the activation pattern from
naturalistic auditory stimulation to the individual PPA localization
with a block-design stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
% reference to supplemental material
Additional analyses of the robustness of the results presented here
are available as supplementary materials.

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14
participants and unilateral right clusters in two participants
\citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for
each naturalistic stimulus and a uniform threshold for all participants.
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrasts, in comparison to the results of a conventional
block-design localizer (unthresholded $Z$-maps are provided on NeuroVault).
% AV
Results of the primary movie contrast yielded bilateral clusters in five participants,
a unilateral right cluster in six participants (of which one participant yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one participant.
% difference to dedicated localizer
We find bilateral clusters for participant \texttt{sub-20}, whereas the block-design
localizer yielded only one cluster in the right hemisphere.
% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine participants that are within or overlapping with the block-design localizer results.
% subj-04
In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
block-design localizer, and movie stimulus yielded only one cluster in the right
hemisphere.
% sub-09
For another participant (\texttt{sub-09}) the analysis yielded one cluster in the
left-hemispheric PPA.
